A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-01-07 src/tex/ms.tex

\begin{itemize}
    \item The turn-over in [O/Fe] evolution due to the second infall epoch produces a peak in the stellar distribution at intermediate [O/Fe], which is not observed in APOGEE.
    \item Attempts to fix the problem with the [O/Fe] distribution in the thin disk end up creating issues with other observables, such as the thick/thin disk surface density ratio, the SN Ia DTD, or the age-metallicity relation.
    \item The equilibrium model, if accurate, places very strict limits on the two-infall model, moreso than for other models.
    \item A short ($\sim200$ Myr) star formation hiatus early in the history of the disk is sufficient to produce a bimodal distribution of [O/Fe] without altering the gas infall prescription.
\end{itemize}

@@

\citet{spitoni_effect_2015}

@@

@@

@@

>>>>

\begin{itemize}
    \item The turn-over in [O/Fe] evolution due to the second infall epoch produces a peak in the stellar distribution at intermediate [O/Fe], which is not observed in APOGEE.
    \item Attempts to fix the problem with the [O/Fe] distribution in the thin disk end up creating issues with other observables, such as the thick/thin disk surface density ratio, the SN Ia DTD, or the age-metallicity relation.
    \item The equilibrium model, if accurate, places very strict limits on the two-infall model, moreso than for other models.
    \item A short ($\sim200$ Myr) star formation hiatus early in the history of the disk is sufficient to produce a bimodal distribution of [O/Fe] without altering the gas infall prescription. This is distinct from the star formation hiatus produced by the two-infall model.
\end{itemize}

@@

\citet{spitoni_effect_2015} add a simple radial migration scheme to the model of \citet{spitoni_effects_2011}. They adopt stellar velocities of $\sim 1$ km s$^{-1}$ and assume that some fixed fraction of stars born at a given radius will end up in the Solar vicinity (10\% of those born at 4 kpc and 20\% at 6 kpc). This mimics the results of previous dynamical models such as \citet{minchev_chemodynamical_2013}. They find that by including stellar migration, they are better able to reproduce the high-metallicity tail of the local metallicity distribution, and they also argue that they constrain the migration speed to $0.5 < v < 2$ km s$^{-1}$ based on this tail. Their only point of comparison with data is the local G-dwarf metallicity distribution.

\citet{grisoni_ambre_2017} argue for a ``parallel'' scenario, where the thick and thin disks form simultaneously but with very different infall timescales (0.1 and 7 Gyr, respectively). They compare their models with stellar abundances from the AMBRE sample of solar-neighborhood dwarfs. They argue that the parallel scenario can produce metal-rich high-alpha stars in situ, whereas in the two-infall scenario these stars would have to migrate from the inner disk.

@@

\citet{spitoni_remind_2024}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/delay_time_distribution.pdf}
    \caption{Caption.}
    \label{fig:dtd}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_sfe_hiatus.pdf}
    \caption{Caption.}
    \label{fig:onezone-sfe-hiatus}
\end{figure}
